Global adjoint tomography -- Model GLAD-M25

### 2018-10-22 main.tex
add south america section

In the North,
we see a high wavespeed craton beneath Greenland which is partly separated from the
North American craton by low wavespeed structures beneath Baffin Bay and the Labrador Sea,
where the North American craton nicely follows the coastline.
In the Northeast corner of the maps we see that the Iceland hotspot is very prominent in GLAD-M25 in all depth ranges, similar to S40RTS but largely missing in S362ANI$+$M.
In the Northwest we see a clear imprint of the Aleutian subduction zone in the 200--400~km depth range, comparable to SL2013NA bu absent in the other global models.

In the East, at 100~km depth,
we see ageing of the Atlantic lithosphere, comparable to the other global models~\citep{muller2008, schaeffer2014imaging}.
All models show fast anomalies beneath Newfoundland and Nova Scotia extending to depths of 300~km.
The Bermuda hotspot shows a very nice slow wavespeed impression,
getting sharper and stronger at depths of 200~km and 300~km (note differences in the scales of the maps).
The Caribbean slab, a relatively young subduction zone, is clearly
visible in our model in the 200--400~km depth range.
At greater depths,
GLAD-M25 shows a very distinct image of the Farallon slab,
but since it goes well beyond the depth range of this comparison,
we return to this feature in Section~\ref{section:slabs}.

@@

\subsubsection{South America}
...to be done...

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M (second column), LLNL-G3Dv3~(third column), and GAP-P4~\citep[last column;][]{fukao2013subducted}.}
\label{fig:southamerica-vp}
\centering
\end{figure}

>>>>

In the North, we see a high wavespeed craton beneath Greenland which is partly
separated from the North American craton by low wavespeed structures beneath
Baffin Bay and the Labrador Sea, where the North American craton nicely follows
the coastline.
In the Northeast corner of the maps we see that the Iceland hotspot is very
prominent in GLAD-M25 in all depth ranges, similar to S40RTS but largely missing
in S362ANI$+$M. In the Northwest we see a clear imprint of the Aleutian
subduction zone in the 200--400~km depth range, comparable to SL2013NA but absent
in the other global models.

In the East, at 100~km depth,
we see ageing of the Atlantic lithosphere, comparable to the other global models
~\citep{muller2008, schaeffer2014imaging}.
All models show fast anomalies beneath Newfoundland and Nova Scotia extending to
depths of 300~km. The Bermuda hotspot shows a very nice slow wavespeed impression,
getting sharper and stronger at depths of 200~km and 300~km (note differences in
the scales of the maps).
The Caribbean slab, a relatively young subduction zone, is clearly
visible in our model in the 200--400~km depth range.
At greater depths,
GLAD-M25 shows a very distinct image of the Farallon slab,
but since it goes well beyond the depth range of this comparison,
we return to this feature in Section~\ref{section:slabs}.

@@

\subsubsection{South America}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M, LLNL-G3Dv3~\citep{}, and GAP-P4~\citep{fukao2013subducted}.}
\label{fig:southamerica-vp}
\centering
\end{figure}

Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, togthere with 3 global models,
S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted}, while the latter two are
global $V_p$ models.

At 100km depth, the northern part of South America is covered by large area
of lithosphere craton, showing fast wave anomaly except GAP-P4. The fast anomaly
stays strong in LLNL-G3Dv3 while for GLAD-M25
and S362ANI+M it disappear at such depth.
At 300km, we are see a sharpened fast anomaly in the south subduction area
in GLAD-M25 compared to S372ANI+M. However, the shape and strength are very close
between GLAD-M25 and LLNL-G3Dv3 models. Moving to even larger depth, the features of
subcutions becomes divergent between the north Peruvian slab and south Chilean slab.
At 600km, we observed a large chunck of fast anomaly in the Chilean slab,
indicating the slab is trapped and stagnant in the mantle transition zone. However,
the Peruvian slabs has penertrated the mantle transition zone and extend till 1000,
reaching the uppermost part of lower mantle, which is consistent with GAP-P4
\citep{fukao2013subducted}.

Besides, in the Pacific and Nazca plate, our models is sharpening the Galapagos,
San Felix and Juan Fernandez hotspot. In the Scotia plate, our models shows a very
strong expression of Scotia Arc subduciton till 1000km, which is barely observable
in other models. In the Carribean plate, we also observed fast anomaly, indicating
the carribean subduction.
